### 2024-06-03 thesis/input_files/probabilistic.tex
final

\section{Quantile forest}
Meinshausen \cite{meinshausen2006quantile} extends the idea of random forest \cite{breiman2001random} generalising it, the result is the quantile forest algorithm. Quantile forest allows us to estimate conditional quantiles in a non parametric fashion.
\\
In order to understand this algorithm, it is first necessary to cover the theory of decision trees and random forests.
\subsection{Decision trees}
Decision tree methods partition recursively the feature space in a set of binary rectangles and then fit a simple model in each of those partitions (the most straightforward is fitting just a constant).
To get started, we first split the space into two disjoint regions, then we model the response variable by the mean of the observed predicted variables with associated features falling in that specific region. Our goal is selecting the best features and best split point to achieve the best generalizing fit.
For a visualisation consider the Figures \ref{fig:elements_statistical_learning1} and \ref{fig:elements_statistical_learning2}, where the decision tree algorithm is visualised for a regression problem with two independent variables $X_1$ and $X_2$.
\begin{figure}
    \includegraphics[width=0.5\textwidth]{images/elsii1.png}
    \caption{Two-dimensional feature space partitioned by recursive binary splitting \cite{hastie2009elements}}
    \label{fig:elements_statistical_learning1}
  \end{figure}
\\
\begin{figure}
\includegraphics[width=1\textwidth]{images/elsii2.png}
\caption{Partition tree and regression model \cite{hastie2009elements}}
\label{fig:elements_statistical_learning2}
\end{figure}
\\
Suppose now to partition the feature space into M regions $R_1,\dots,R_M$, then the model reads as follows.
\begin{equation}
    f(x)=\sum\limits_{m=1}^{M}c_m\mathbb{I}_{\{x \in R_m\}}
\end{equation}
\\
It follows that the function minimising the sum of squares is the one with $\hat{c}_m=mean(y_i|x_i \in R_m)$.
Finding the best split in terms of minimum sum of squares is computationally infeasible in practice. Therefore we approximate a solution by approaching the problem in a greedy fashion.
Let $j$ denote the splitting variable and $s$ be the split point we define the two half planes
\begin{equation}
    R_1(j,s)=\{X|X_j\leq s\} \quad R_2(j,s)=\{X|X_j >s\}
\end{equation}
Then we search for the $s$ and $j$ that solve
\begin{equation}
    \min_{j,s}\left[\min_{c_1} \sum\limits_{x_i \in R_1(j,s)}(y_i-c_1)^2+\min_{c_2} \sum\limits_{x_i \in R_2(j,s)}(y_i-c_2)^2\right]
\end{equation}
The inner problem is easy, as already pointed out, we will have 
\begin{equation}
    \hat{c}_1=mean(y_i|x_i \in R_1) \quad \hat{c}_2=mean(y_i|x_i \in R_2)
\end{equation}
For the outer problem, we scan through all the $(j,s)$ tuples and pick the best pair. 
Next, one or both of these regions from the previous step are split into two more regions. We recurse this process until some stopping condition is triggered (max number of branches, max depth of tree, threshold on the mean squared error (MSE), minimum number of observations in each leaf node).
Notice, this being a greedy algorithm implies that our final solution is guaranteed to be just a local optimum not a global one.
Even though their simplicity, these models have proved themselves to be really powerful. See Figure \ref{fig:decision_tree} for an example where decision trees with different hyperparameters are fitted to a sine wave plus noise. The most popular among these models is the CART \cite{breiman2017classification} tree, its name comes from the fact that it can handle both classification and regression problems.
\begin{figure}
    \includegraphics[width=\textwidth]{images/decision_tree.png}
    \caption{Decision tree regression}
    \label{fig:decision_tree}
    % image generated on coolab to be quick
\end{figure}

@@

    &\alpha^\intercal\mathbb{1}=1

@@

Since our optimisation problem possesses strong duality and it is differentiable in both the objective and the constraint, we have that it must satisfy the Karush Kuhn Tucker conditions (KKT), see Section 5.5.3 \cite{boyd2004convex}.

@@

\begin{table}[!h]
    \caption{Pinball loss quantile-wise for Melbourne data}
    \begin{tabular}{lllll}
    \toprule
    Quantiles & Linear qr & Gbm qr & Quantile forest & KQR \\
    \midrule
    0.100000 & 0.710644 & 0.549232 & 0.562888 & \textbf{0.540145} \\
    0.200000 & 1.155014 & 0.938561 & 0.946712 & \textbf{0.903193} \\
    0.300000 & 1.417805 & 1.212671 & 1.222407 & \textbf{1.173627} \\
    0.400000 & 1.540108 & 1.399925 & 1.409293 & \textbf{1.368022} \\
    0.500000 & 1.574957 & 1.517281 & 1.484589 & \textbf{1.456053} \\
    0.600000 & 1.525114 & 1.498608 & 1.495474 & \textbf{1.447470} \\
    0.700000 & 1.397918 & 1.372183 & 1.362173 & \textbf{1.331375} \\
    0.800000 & 1.170140 & 1.115077 & 1.123195 & \textbf{1.096649} \\
    0.900000 & 0.787195 & \textbf{0.714075} & 0.734112 & 0.715013 \\
    \bottomrule
    \end{tabular}
\end{table}
As already pointed out, the quantile regression with $q=0.5$ corresponds to the standard regression problem, hence we can compare the proposed methods also in terms of the mean absolute error.
\begin{table}[!h]
\caption{Mean absolute error for Melbourne data}
\begin{tabular}{lllll}
    \toprule
     & Linear qr & Gbm qr & Quantile forest & KQR \\
    \midrule
    MAE & 3.253882 & 3.134805 & 3.095041 & \textbf{3.024305} \\
    \bottomrule
    \end{tabular}
\end{table}  
From these tables, we can see that kernel quantile regression outperformes the simple quantile regressor as well as the more complex models like quantile forest and gradient boosting quantile regression for the Melbourne temperatures dataset. Not only kernel quantile regression was the best in terms of total pinball loss but also the best in terms of each quantile pinball loss and mean absolute error.
Comparison has been carried out on further datasets, yielding similar conclusions as the one of above, to know more see Appendix \ref{appendix:quantile_regressor_extensive_comparison}.

@@

From these tables, we can conclude that the Matern and the Chi squared kernels are the top performers on the Melbourne weather data. Finally, the equaility in the scores of the Absolute Laplacian and the Matern 0.5 follows from the fact that regressors are one dimensional for the Melbourne weather data.
% tables
\begin{table}[!h]
    \caption{Kernels comparison pinball loss for Melbourne data}
    \label{tab:kernel pinball comparison}
    \begin{center}
    \begin{tabular}{lll}
        \toprule
        & Kernel & Pinball loss
        \\
        \midrule
        & Absolute Laplacian &  10.136551 \\
        & Matern 0.5/Laplacian & 10.136551  \\
        & Matern 1.5 & 10.082668  \\
        & Matern 2.5 & 10.0494190    \\

>>>>

\section{Quantile forest}
Meinshausen \cite{meinshausen2006quantile} extends the idea of random forest \cite{breiman2001random} generalising it, the result is the quantile forest algorithm. Quantile forest allows us to estimate conditional quantiles in a non parametric fashion.
\\
In order to understand this algorithm, it is first necessary to cover the theory of decision trees and random forests.
\subsection{Decision trees}
Decision tree methods partition recursively the feature space in a set of binary rectangles and then fit a simple model in each of those partitions (the most straightforward is fitting just a constant).
To get started, we first split the space into two disjoint regions, then we model the response variable by the mean of the observed predicted variables with associated features falling in that specific region. Our goal is selecting the best features and best split point to achieve the best generalising fit.
For a visualisation consider the Figures \ref{fig:elements_statistical_learning1} and \ref{fig:elements_statistical_learning2}, where the decision tree algorithm is visualised for a regression problem with two independent variables $X_1$ and $X_2$.
\begin{figure}
    \includegraphics[width=0.5\textwidth]{images/elsii1.png}
    \caption{Two-dimensional feature space partitioned by recursive binary splitting \cite{hastie2009elements}}
    \label{fig:elements_statistical_learning1}
  \end{figure}
\\
\begin{figure}
\includegraphics[width=1\textwidth]{images/elsii2.png}
\caption{Partition tree and regression model \cite{hastie2009elements}}
\label{fig:elements_statistical_learning2}
\end{figure}
\\
Suppose now to partition the feature space into M regions $R_1,\dots,R_M$, then the model reads as follows.
\begin{equation}
    f(x)=\sum\limits_{m=1}^{M}c_m\mathbb{I}_{\{x \in R_m\}}
\end{equation}
\\
It follows that the function minimising the sum of squares is the one with $\hat{c}_m=mean(y_i|x_i \in R_m)$.
Finding the best split in terms of minimum sum of squares is computationally infeasible in practice. Therefore, we approximate a solution by approaching the problem in a greedy fashion.
Let $j$ denote the splitting variable and $s$ be the split point we define the two half planes
\begin{equation}
    R_1(j,s)=\{X|X_j\leq s\} \quad R_2(j,s)=\{X|X_j >s\}
\end{equation}
Then we search for the $s$ and $j$ that solve
\begin{equation}
    \min_{j,s}\left[\min_{c_1} \sum\limits_{x_i \in R_1(j,s)}(y_i-c_1)^2+\min_{c_2} \sum\limits_{x_i \in R_2(j,s)}(y_i-c_2)^2\right]
\end{equation}
The inner problem is easy, as already pointed out, we will have 
\begin{equation}
    \hat{c}_1=mean(y_i|x_i \in R_1) \quad \hat{c}_2=mean(y_i|x_i \in R_2)
\end{equation}
For the outer problem, we scan through all the $(j,s)$ tuples and pick the best pair. 
Next, one or both of these regions from the previous step are split into two more regions. We recurse this process until some stopping condition is triggered (max number of branches, max depth of tree, threshold on the mean squared error (MSE), minimum number of observations in each leaf node).
Notice, this being a greedy algorithm implies that our final solution is guaranteed to be just a local optimum not a global one.
Even though their simplicity, these models have proved themselves to be really powerful. See Figure \ref{fig:decision_tree} for an example where decision trees with different hyperparameters are fitted to a sine wave plus noise. The most popular among these models is the CART \cite{breiman2017classification} tree, its name comes from the fact that it can handle both classification and regression problems.
\begin{figure}
    \includegraphics[width=\textwidth]{images/decision_tree.png}
    \caption{Decision tree regression}
    \label{fig:decision_tree}
    % image generated on coolab to be quick
\end{figure}

@@

    &\alpha^\intercal\mathbb{1}=0

@@

Since our optimisation problem possesses strong duality and it is differentiable in both the objective and the constraint, we have that it must satisfy the Karush Kuhn Tucker conditions (KKT), see \cite[Section 5.5.3]{boyd2004convex}.

@@

\begin{table}[!h]
    \caption{Pinball loss quantile-wise for Melbourne data}
    \begin{tabular}{lllll}
    \toprule
    Quantiles & Linear qr & Gbm qr & Quantile forest & KQR \\
    \midrule
    0.1 & 0.710644 & 0.549232 & 0.562888 & \textbf{0.540145} \\
    0.2 & 1.155014 & 0.938561 & 0.946712 & \textbf{0.903193} \\
    0.3 & 1.417805 & 1.212671 & 1.222407 & \textbf{1.173627} \\
    0.4 & 1.540108 & 1.399925 & 1.409293 & \textbf{1.368022} \\
    0.5 & 1.574957 & 1.517281 & 1.484589 & \textbf{1.456053} \\
    0.6 & 1.525114 & 1.498608 & 1.495474 & \textbf{1.447470} \\
    0.7 & 1.397918 & 1.372183 & 1.362173 & \textbf{1.331375} \\
    0.8 & 1.170140 & 1.115077 & 1.123195 & \textbf{1.096649} \\
    0.9 & 0.787195 & \textbf{0.714075} & 0.734112 & 0.715013 \\
    \bottomrule
    \end{tabular}
\end{table}
As already pointed out, the quantile regression with $q=0.5$ corresponds to the standard regression problem, hence we can compare the proposed methods also in terms of the mean absolute error.
\begin{table}[!h]
\caption{Mean absolute error for Melbourne data}
\begin{tabular}{lllll}
    \toprule
     & Linear qr & Gbm qr & Quantile forest & KQR \\
    \midrule
    MAE & 3.253882 & 3.134805 & 3.095041 & \textbf{3.024305} \\
    \bottomrule
    \end{tabular}
\end{table}  
From these tables, we can see that kernel quantile regression outperforms the simple quantile regressor as well as the more complex models like quantile forest and gradient boosting quantile regression for the Melbourne temperatures dataset. Not only kernel quantile regression was the best in terms of total pinball loss but also the best in terms of each quantile pinball loss and mean absolute error.
Comparison has been carried out on further datasets, yielding similar conclusions as the one of above, to know more see Appendix \ref{appendix:quantile_regressor_extensive_comparison}.

@@

From these tables, we can conclude that the Matern and the Chi squared kernels are the top performers on the Melbourne weather data. Finally, the equality in the scores of the Absolute Laplacian and the Matern 0.5 follows from the fact that regressors are one dimensional for the Melbourne weather data.
% tables
\begin{table}[!h]
    \caption{Kernels comparison pinball loss for Melbourne data}
    \label{tab:kernel pinball comparison}
    \begin{center}
    \begin{tabular}{lll}
        \toprule
        & Kernel & Pinball loss
        \\
        \midrule
        & Absolute Laplacian &  10.136551 \\
        & Matern 0.5/Laplacian & 10.136551  \\
        & Matern 1.5 & 10.082668  \\
        & Matern 2.5 & 10.0494190    \\

### 2024-06-03 thesis/input_files/problemdescription.tex
final

Individuals and organisations constantly face situations of uncertainty, thus the need for robust forecasting methods. Such methods are crucial in the process of taking informed decisions and for strategic planning.
\\
The basic idea of forecasting is that we can extract knowledge from the past in order to make educated guesses about the future. Consequently, the range of fields where forecasting can be applied is very wide.
In this thesis, our focus lies on applying forecasting techniques to the energy sector. 
\\
Our decision to focus on the energy market is mainly motivated by the rapid changes it has undergone. %/experienced 
Over the last decades, electricity markets have gone through an unprecedented transformation. This shift was driven by the liberalisation of such markets, the development and integration of renewable energy sources, the  increase of low carbon technologies and the adoption of smart meters. Events like the California electricity crisis are further motivating the choice of the electricity sector as subject of our studies, see \cite{california}.
Moreover, the process of deregulation lead to an increasing interest in the field of electricity forecasting (EF) within the academic community, see Figure \ref{fig:epf_evolution}.
In addtion, the United Nations have identified the right to access affordable, reliable, sustainable and modern energy as one of their 17 sustainable development goals (SDGs) \citeW{un_sdgs}.
Finally, the electricity market has a set of features that make it unique: electricity cannot be stored in an efficient way and supply and demand have to be matched instantly.
\\
\section{Motivation}
There are mutliple reasons why the energy sector needs robust forecasting techniques.
For power market companies, being able to predict prices with a low mean absolute percentage error (MAPE) \ref{mape} results in increased savings \cite{savings}. Furthermore, the adoption of smart meters provides power market companies with a huge amount of consumer data. This enables them to better model consumer preferences.
\\
Transmission system operators' (TSO) main goal is to match supply and demand, generally TSO do so by increasing or decreasing the generation. Thus, from their point of view forecasting is critical for balancing the electricity network.
Probabilistic forecasting may be useful to power producers, traders and consumers in order to improve their decision making process and managing risk. This holds in particular for traders, because probabilistic forecasts enable them to simulate scenarios and carry out stress tests.
Other possible applications include: control of storage, demand side response, anomaly detection, network design and planning, simulating inputs and handling missing data.
\\
\section{Point versus probabilistic forecast}
A distinction has to be made between two types of forecasting approaches: point forecasts and probabilistic forecasts.
Point prediction, also called deterministic forecasting in the literature \cite{EPF_review}, is all about predicting a particular value in time.
On the other hand, with probabilistic forecasting we aim at predicting either an interval, quantiles or a probability distribution for each point in time \cite{nowotarski}. For this reason, probabilistic forecasts are more informative than point forecasts. This is why the interest of the research community is shifting towards them.
A probabilistic forecast can be turned into a point forecast by simply taking its expectation.
Alternatively, a probabilistic forecast can be derived from a point one by modeling the residuals of the point prediction.

@@

The scope of the thesis is analyzing state of the art forecasting methods in the energy market and to compare and to integrate them with ideas coming from the theory of kernel methods.

\section{Outline}
We start with a literature review and a bibliometric analysis in Section \ref{literature_review}.
Then, the theory underlying kernel methods is covered in Section \ref{kernel_theory}. Evaluation metrics necessary to rank the forecasting techniques are presented in Section \ref{metrics}. Section \ref{energy_market} explains the core features and terminology of the energy market and of the electricity newtork.
Following, Sections \ref{ch:point} and \ref{ch:prob} introduce the state of the art methods in the context of point and probabilistic forecasting respectively.
Section \ref{eda} goes on with the extract-load-transform (ETL) pipeline and the exploratory data analysis (EDA). 
Implementation details are included in Section \ref{implementation}.
Finally, Section \ref{analysis} presents experiments results and discusses models' strenghts, weaknesses and possible improvements.

>>>>

Individuals and organisations constantly face situations of uncertainty, thus the need for robust forecasting methods. Such methods are crucial in the process of taking informed decisions and for strategic planning.
\\
The basic idea of forecasting is that we can extract knowledge from the past in order to make educated guesses about the future. Consequently, the range of fields where forecasting can be applied is very wide.
In this thesis, our focus lies on applying forecasting techniques to the energy sector. 
\\
Our decision to focus on the energy market is mainly motivated by the rapid changes it has undergone. %/experienced 
Over the last decades, electricity markets have gone through an unprecedented transformation. This shift was driven by the liberalisation of such markets, the development and integration of renewable energy sources, the  increase of low carbon technologies and the adoption of smart meters. Events like the California electricity crisis are further motivating the choice of the electricity sector as subject of our studies, see \cite{california}.
Moreover, the process of deregulation led to an increasing interest in the field of electricity forecasting (EF) within the academic community, see Figure \ref{fig:epf_evolution}.
In addtion, the United Nations have identified the right to access affordable, reliable, sustainable and modern energy as one of their 17 sustainable development goals (SDGs) \citeW{un_sdgs}.
Finally, the electricity market has a set of features that make it unique: electricity cannot be stored in an efficient way and supply and demand have to be matched instantly.
\\
\section{Motivation}
There are mutliple reasons why the energy sector needs robust forecasting techniques.
For power market companies, being able to predict prices with a low mean absolute percentage error (MAPE), see Section \ref{mape}, results in increased savings \cite{savings}. Furthermore, the adoption of smart meters provides power market companies with a huge amount of consumer data. This enables them to better model consumer preferences.
\\
Transmission system operators' (TSO) main goal is to match supply and demand, generally TSO do so by increasing or decreasing the generation. Thus, from their point of view forecasting is critical for balancing the electricity network.
Probabilistic forecasting may be useful to power producers, traders and consumers in order to improve their decision making process and managing risk. This holds in particular for traders, because probabilistic forecasts enable them to simulate scenarios and carry out stress tests.
Other possible applications include: control of storage, demand side response, anomaly detection, network design and planning, simulating inputs and handling missing data.
\\
\section{Point versus probabilistic forecast}
A distinction has to be made between two types of forecasting approaches: point forecasts and probabilistic forecasts.
Point prediction, also called deterministic forecasting in the literature \cite{EPF_review}, is all about predicting a particular value in time.
On the other hand, with probabilistic forecasting we aim at predicting either an interval, quantiles or a probability distribution for each point in time \cite{nowotarski}. For this reason, probabilistic forecasts are more informative than point forecasts. This is why the interest of the research community is shifting towards them.
A probabilistic forecast can be turned into a point forecast by simply taking its expectation.
Alternatively, a probabilistic forecast can be derived from a point one by modelling the residuals of the point prediction.

@@

The scope of the thesis is analysing state of the art forecasting methods in the energy market and to compare and to integrate them with ideas coming from the theory of kernel methods.

\section{Outline}
We start with a literature review and a bibliometric analysis in Section \ref{literature_review}.
Then, the theory underlying kernel methods is covered in Section \ref{kernel_theory}. Evaluation metrics necessary to rank the forecasting techniques are presented in Section \ref{metrics}. Section \ref{energy_market} explains the core features and terminology of the energy market and of the electricity network.
Following, Sections \ref{ch:point} and \ref{ch:prob} introduce the state of the art methods in the context of point and probabilistic forecasting respectively.
Section \ref{eda} goes on with the extract-load-transform (ETL) pipeline and the exploratory data analysis (EDA). 
Implementation details are included in Section \ref{implementation}.
Finally, Section \ref{analysis} concludes this thesis presenting and commenting experiments results.
% and discusses models' strenghts, weaknesses and possible improvements.

### 2024-06-03 thesis/input_files/qr.tex
final

Quantile regression can be interpreted as an extension of standard regression. In this setting, one slices the dependent variables into quantiles and then fits a regression for each quantile. With standard regression, we build a model for the conditional mean, conversely, with quantile regression we model the conditional quantile function for any desired quantile. 
Therefore, with quantile regression we are able to study the impact of covariates on quantiles directly.
\begin{definition}
    For any real valued random variable Y, we define its associated quantile function.
    \begin{equation}
        Q_q=\inf\{y:F(y)\geq q\}
    \end{equation}
\end{definition}
Alternatively, in order  to ease the posing of the quantile regression problem, we can formulate quantiles as the solutions to the following optimisation problems.
\\
For any $0<q<1$ consider the pinball loss function from Section \ref{pinball}, $\rho_q(u)=u(q-\mathbb{I}_{\{u<0\}})$. 
Such loss is minimized by the quantile $Q_q$.
 we can estimate quantiles by minimizing the expectation of $\rho_q(y-g(x,\beta))$ with respect to the parameter $\beta$.
\\
Note, that in the special case $q=\frac{1}{2}$,  quantile regression corresponds exactly to standard regression with an absolute value loss function.
\\
It follows that the conditional linear quantile function $\hat{Q}_q=x_i\beta(q)$, can be estimated by solving
\begin{equation}\label{eq:linear_quantile_regression_minimisation_problem}
    \hat{\beta}(q)=\argmin{\beta}\sum\limits_{i=1}^n \rho_q   (y_i-x_i \beta)
\end{equation}
\\
Notice that, this cost function is not differentiable, therefore there is no analytical solution to the quantile regression problem. Nevertheless, we can easily solve it by employing linear programming and convex optimisation \cite{boyd2004convex}.
\\
Furthermore, we can extend this framework to non linear quantile regression by choosing a non linear model in place of $x\beta$ in the above Equation \ref{eq:linear_quantile_regression_minimisation_problem}.
% \\
% In order to illustrate the approach, let us consider applying quantile regression to the maximum daily temperature dataset in Melbourne \cite{hyndman1996estimating}; models considered will be linear, gradient boosting machine, quantile forest\cite{meinshausen2006quantile} and kernel quantile regression.
% - se si puo fare plot con stessi dati ma differenti f nel quantile regression

>>>>

Quantile regression can be interpreted as an extension of standard regression. In this setting, one slices the dependent variables into quantiles and then fits a regression for each quantile. With standard regression, we build a model for the conditional mean, conversely, with quantile regression we model the conditional quantile function for any desired quantile. 
Therefore, with quantile regression we are able to study the impact of covariates on quantiles directly.
\begin{definition}
    For any real valued random variable Y, we define its associated quantile function.
    \begin{equation}
        Q_q=\inf\{y:F(y)\geq q\}
    \end{equation}
\end{definition}
Alternatively, in order  to ease the posing of the quantile regression problem, we can formulate quantiles as the solutions to the following optimisation problems.
\\
For any $0<q<1$ consider the pinball loss function from Section \ref{pinball}, $\rho_q(u)=u(q-\mathbb{I}_{\{u<0\}})$. 
Such loss is minimised by the quantile $Q_q$.
 we can estimate quantiles by minimising the expectation of $\rho_q(y-g(x,\beta))$ with respect to the parameter $\beta$.
\\
Note, that in the special case $q=\frac{1}{2}$,  quantile regression corresponds exactly to standard regression with an absolute value loss function.
\\
It follows that the conditional linear quantile function $\hat{Q}_q=x_i\beta(q)$, can be estimated by solving
\begin{equation}\label{eq:linear_quantile_regression_minimisation_problem}
    \hat{\beta}(q)=\argmin{\beta}\sum\limits_{i=1}^n \rho_q   (y_i-x_i \beta)
\end{equation}
\\
Notice that, this cost function is not differentiable, therefore there is no analytical solution to the quantile regression problem. Nevertheless, we can easily solve it by employing linear programming and convex optimisation \cite{boyd2004convex}.
\\
Furthermore, we can extend this framework to non linear quantile regression by choosing a non linear model in place of $x\beta$ in the above Equation \ref{eq:linear_quantile_regression_minimisation_problem}.
% \\
% In order to illustrate the approach, let us consider applying quantile regression to the maximum daily temperature dataset in Melbourne \cite{hyndman1996estimating}; models considered will be linear, gradient boosting machine, quantile forest\cite{meinshausen2006quantile} and kernel quantile regression.
% - se si puo fare plot con stessi dati ma differenti f nel quantile regression

### 2024-06-03 thesis/input_files/symbols.tex
May 15th 2024
thesis update
May 25 2024
corrected all comments
final

%G
\glsxtrnewsymbol[description={Generalized additive models}]{GAMs}{GAMs}
\glsxtrnewsymbol[description={Gradient boosting regression tree}]{GBRT}{GBRT}
\glsxtrnewsymbol[description={Global energy forecasting competition}]{GEFCom}{GEFCom}
\glsxtrnewsymbol[description={Gaussian process regression}]{GPR}{GPR}

@@

%R
\glsxtrnewsymbol[description={Random forest}]{RF}{RF}
\glsxtrnewsymbol[description={Reproducing kernel hilbert space}]{RKHS}{RKHS}
\glsxtrnewsymbol[description={Root mean squared error}]{RMSE}{RMSE}

%P
\glsxtrnewsymbol[description={Partial autocorrelation function}]{PACF}{PACF}
\glsxtrnewsymbol[description={Power exchange}]{PX}{PX}
\glsxtrnewsymbol[description={Prediction interval}]{PI}{PI}
\glsxtrnewsymbol[description={Price Forecasting}]{PF}{PF}

@@

%MATHEMATICAL NOTATION
% D
\glsxtrnewsymbol[description={dual optimum}]{d^*}{\ensuremath{d^*}}

@@

\glsxtrnewsymbol[description={feature space}]{F}{\ensuremath{F}}

@@

% I
\glsxtrnewsymbol[description={Indicator function}]{mathbb{I}}{\ensuremath{\mathbb{I}}}

@@

% L
\glsxtrnewsymbol[description={lagrangian}]{L}{\ensuremath{L}}

@@

\glsxtrnewsymbol[description={reproducing kernel hilbert space}]{H}{\ensuremath{\mathcal{H}}}

% T
\glsxtrnewsymbol[description={Tensor product}]{otimes}{\ensuremath{\otimes}}

>>>>

%G
\glsxtrnewsymbol[description={Generalised additive models}]{GAMs}{GAMs}
\glsxtrnewsymbol[description={Gradient boosting regression tree}]{GBRT}{GBRT}
\glsxtrnewsymbol[description={Global energy forecasting competition}]{GEFCom}{GEFCom}
% \glsxtrnewsymbol[description={Gaussian process regression}]{GPR}{GPR}

@@

%R
\glsxtrnewsymbol[description={Random forest}]{RF}{RF}
\glsxtrnewsymbol[description={Reproducing kernel Hilbert space}]{RKHS}{RKHS}
\glsxtrnewsymbol[description={Root mean squared error}]{RMSE}{RMSE}
\glsxtrnewsymbol[description={Run of river}]{ROR}{ROR}

%P
\glsxtrnewsymbol[description={Pattern analysis}]{PA}{PA}
\glsxtrnewsymbol[description={Partial autocorrelation function}]{PACF}{PACF}
\glsxtrnewsymbol[description={Power exchange}]{PX}{PX}
\glsxtrnewsymbol[description={Prediction interval}]{PI}{PI}
\glsxtrnewsymbol[description={Price Forecasting}]{PF}{PF}

@@

%MATHEMATICAL NOTATION
% D
\glsxtrnewsymbol[description={direct sum}]{oplus}{\ensuremath{\oplus}}
\glsxtrnewsymbol[description={dual optimum}]{d^*}{\ensuremath{d^*}}

@@

\glsxtrnewsymbol[description={feature space}]{F}{\ensuremath{\mathcal{F}}}

@@

% I
\glsxtrnewsymbol[description={indicator function}]{mathbb{I}}{\ensuremath{\mathbb{I}}}

@@

% L
\glsxtrnewsymbol[description={Lagrangian}]{L}{\ensuremath{\mathcal{L}}}

@@

\glsxtrnewsymbol[description={reproducing kernel Hilbert space}]{H}{\ensuremath{\mathcal{H}}}

% T
\glsxtrnewsymbol[description={tensor product}]{otimes}{\ensuremath{\otimes}}
